Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2020-12-16 analysis/pre-print/pre-print.Rmd
Pre-print

---
title: Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

authors: 
  - name: Elio Campitelli
    email: elio.campitelli@cima.fcen.uba.ar
  - name:  Leandro B. Díaz
  - name:  Carolina Vera

@@

keywords:
  - Southern Annular Mode
  - general circulation
  - zonally asymmetric circulation
  - El Niño Southern Oscillation
bibliography: "AsymSAM,packages"
bibstyle: "plainnat"
output: 
 bookdown::pdf_book: 
    base_format: rticles::arxiv_article
    latex_engine: "xelatex"
    citation_package: "natbib"
    keep_tex: true
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
 - \usepackage{amsmath}
#  - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 - \usepackage{natbib}    
---

```{r setup, echo = FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.extra = 41,
  cache.path = "../cache/pre-print",
  collapse = TRUE,
  comment = "#>",
  dev = "pdf",
  # dpi = 300,
  out.extra = ""
)

@@

# Acknowledgements

>>>>

---
title: Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach
authors:
  - name:  Elio Campitelli
    affiliation: |
      UBA - FCEN - DCAO
    email: elio.campitelli@cima.fcen.uba.ar
  - name:  Leandro Díaz
    affiliation: |
      UBA - FCEN - DCAO
  - name:  Carolina Vera
    affiliation: |
      UBA - FCEN - DCAO

@@

keywords:
  - Southern Annular Mode
  - general circulation
  - zonally asymmetric circulation
  - El Niño Southern Oscillation

notice: "This is a non-peer reviewed preprint submitted to EarthArXiv. The manuscript is under review at Climate Dynamics. Subsequent versions of this article may have different content"

bibliography: "AsymSAM,packages"
biblio-style: plainnat
output: 
  bookdown::pdf_document2:
      template: "template.tex"
      latex_engine: "xelatex"
      citation_package: "natbib"
      keep_tex: true
  bookdown::pdf_book: 
      base_format:  rticles::arxiv_article
      latex_engine: "xelatex"
      citation_package: "natbib"
      keep_tex: true
      # pandoc_args: ["--lua-filter=abstract-to-meta.lua"]
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
 - \usepackage{amsmath}
#  - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 - \usepackage[round]{natbib}
 - \hypersetup{hidelinks}
---

```{r setup, echo = FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.extra = 42,
  cache.path = "../cache/pre-print",
  collapse = TRUE,
  comment = "#>",
  dev = "pdf",
  # dpi = 300,
  out.extra = ""
)

@@

# Acknowledgements {-}
